Assessing the impacts of time to detection distribution assumptions on detection probability estimation

### 2017-07-31 Supplement.tex
Remove commented packages
Use graphicspath

\documentclass[useAMS,usenatbib,referee,12pt]{article}
\usepackage[margin=1.0in]{geometry}
%\usepackage{amsmath}
%\usepackage{amssymb}
%\usepackage{amsfonts}
%\usepackage{parskip}
%\usepackage[round]{natbib}
%\usepackage{caption}
%\usepackage{tabularx, booktabs}
%\usepackage{float}
\usepackage{placeins}     % Enables \FloatBarrier, which enforces a break between table/figures
%\usepackage{adjustbox}
\usepackage{multirow}     % Allows tables with vertically merged cells
%\usepackage{setspace}
%\usepackage{url}
\usepackage{xr}    % Links to external document
%\usepackage{listings}
%\usepackage{verbatim}
%\usepackage{graphicx}
\usepackage{rotating}     % For landscape-oriented table

@@

\newcommand{\pdet}{p^{(det)}}
% Plug-in caption for figures created using \sfig
\newcommand{\capt}[1]{Caterpillar plots of posterior parameter estimates from all models fit to the simulated #1 dataset (from simulations involving covariates and random effects).  Black and orange lines depict central 95\% and 50\% credible intervals, respectively.  The black dot is the posterior meadian.  The blue 'X' is the true parameter value and is positioned on the correctly specified model.  $\beta$'s are fixed effect parameters, $\sigma$'s are random effect standard deviations, and $\gamma$ is a mixing parameter.  Parameters designated with an 'A' are abundance parameters; those designated with a 'D' are detection parameters.}
% Include graphics for posterior estimates of dataset parameters
\newcommand{\sfig}[2]{\begin{figure}
  \includegraphics[width=1.0\textwidth]{Sims/SimFull/Posteriors_all_simdat#2.jpg} % Source file: Sims/SimFull/Outputs_Code_sf.R
  \caption{\capt{#1}}
  \end{figure}
}
\renewcommand{\thesection}{S-\arabic{section}}   % Label section with 'S-#'
\renewcommand{\thetable}{S-\arabic{table}}
\renewcommand{\thefigure}{S-\arabic{figure}}

@@

\vspace{1.2cm}
% Note: both tables are in the same 'table' environment.

@@

\begin{figure}[h!]\centering
\includegraphics[width=0.98\textwidth]{Sims/SimFull/pdet_cater_family} % Source file: Sims/SimFull/Outputs_Code_sf.R
\caption{\label{pdet_cater_family}  Simulation results from Section \ref{M-sec:simfull}.
Caterpillar plots of posterior 50\% (orange) and 95\% (black) credible intervals for the probability of detection $\pdet$ across all surveys.
Data and models include fixed and random effects for both abundance and detection processes.
All data and inference models include mixture components.  
Each plot presents one simulated dataset.  
`X' marks the expected marginal probability of detection based on true parameter values.}
\end{figure}

\subsection{Posteriors parameter estimates from simulations including covariates and random effects}\label{s:sim3}
\sfig{non-mixture exponential}{1}
\sfig{exponential mixture}{2}
\sfig{nonpeaked non-mixture gamma}{3}
\sfig{nonpeaked gamma mixture}{4}
\sfig{peaked non-mixture gamma}{5}
\sfig{peaked gamma mixture}{6}
\sfig{nonpeaked non-mixture lognormal}{7}
\sfig{nonpeaked lognormal mixture}{8}
\sfig{peaked non-mixture lognormal}{9}
\sfig{peaked lognormal mixture}{10}
\sfig{nonpeaked non-mixture Weibull}{11}
\sfig{nonpeaked Weibull mixture}{12}
\sfig{peaked non-mixture Weibull}{13}
\sfig{peaked Weibull mixture}{14}

>>>>

\documentclass[useAMS,usenatbib,referee,12pt]{article}
\usepackage[margin=1.0in]{geometry}
\usepackage{placeins}     % Enables \FloatBarrier, which enforces a break between table/figures
\usepackage{multirow}     % Allows tables with vertically merged cells
\usepackage{xr}    % Links to external document
\usepackage{rotating}     % For landscape-oriented table

\graphicspath{{Sims/SimFull/}}

@@

\newcommand{\pdet}{p^{(det)}}
\newcommand{\capt}[1]{Caterpillar plots of posterior parameter estimates from all models fit to the simulated #1 dataset (from simulations involving covariates and random effects).  Black and orange lines depict central 95\% and 50\% credible intervals, respectively.  The black dot is the posterior meadian.  The blue 'X' is the true parameter value and is positioned on the correctly specified model.  $\beta$'s are fixed effect parameters, $\sigma$'s are random effect standard deviations, and $\gamma$ is a mixing parameter.  Parameters designated with an 'A' are abundance parameters; those designated with a 'D' are detection parameters.}
\newcommand{\sfig}[2]{\begin{figure}
  \includegraphics[width=1.0\textwidth]{Posteriors_all_simdat#2.jpg} % Source file: Sims/SimFull/Outputs_Code_sf.R
  \caption{\capt{#1}}
  \end{figure}
}
\renewcommand{\thesection}{S-\arabic{section}}   % Label section with 'S-#'
\renewcommand{\thetable}{S-\arabic{table}}
\renewcommand{\thefigure}{S-\arabic{figure}}

@@

@@

\begin{figure}[h!]\centering
\includegraphics[width=0.98\textwidth]{pdet_cater_family} % Source file: Sims/SimFull/Outputs_Code_sf.R
\caption{\label{pdet_cater_family}  Simulation results from Section \ref{M-sec:simfull}.
Caterpillar plots of posterior 50\% (orange) and 95\% (black) credible intervals for the probability of detection $\pdet$ across all surveys.
Data and models include fixed and random effects for both abundance and detection processes.
All data and inference models include mixture components.  
Each plot presents one simulated dataset.  
`X' marks the expected marginal probability of detection based on true parameter values.}
\end{figure}

\subsection{Posterior parameter estimates from simulations including covariates and random effects}\label{s:sim3}
\sfig{non-mixture exponential}{1}
\sfig{exponential mixture}{2}
\sfig{nonpeaked non-mixture gamma}{3}
\sfig{nonpeaked gamma mixture}{4}
\sfig{peaked non-mixture gamma}{5}
\sfig{peaked gamma mixture}{6}
\sfig{nonpeaked non-mixture lognormal}{7}
\sfig{nonpeaked lognormal mixture}{8}
\sfig{peaked non-mixture lognormal}{9}
\sfig{peaked lognormal mixture}{10}
\sfig{nonpeaked non-mixture Weibull}{11}
\sfig{nonpeaked Weibull mixture}{12}
\sfig{peaked non-mixture Weibull}{13}
\sfig{peaked Weibull mixture}{14}
